Trigger is a crucial item in experiments at hadron colliders. In this thesis,  
a software profiling tool has been developed, which helps to analyze and improve the 
performance of the High Level Trigger software of the \lhcb experiment. 
This tool is able to identify spots where the execution time of the trigger application is slow, 
thereby allowing the optimization of the trigger decision speed and minimizing dead times 
during data taking. 

The highly efficient \lhcb trigger allows precision studies 
of decays of heavy flavoured particles in final states with muons.  
In this thesis, a study of \chib production at \lhcb is performed on a proton-proton collisions data set, 
corresponding to 3\invfb integrated luminosity, collected
at center-of-mass energies of \sqs=7 and 8 TeV. Radiative \chib transitions to
\Y1S, \Y2S and \Y3S are reconstructed, where the $\Upsilon(nS)$, indicated generally as $\Upsilon$ in the following, decays in two muon. 
The fraction of $\Upsilon$ originating from \chib decays
are measured as a function of $\Upsilon$ transverse momentum in the \lhcb rapidity range
$2.0 < y^{\Upsilon} < 4.5$. The analyzed transverse momentum ranges for decays
to \Y1S, \Y2S and \Y3S are $6<p_T^{\Y1S}<40\gevc$, $18<p_T^{\Y2S}<40\gevc$ and
$27<p_T^{\Y3S}<40\gevc$, respectively. The measurement of
\Y3S fractions in radiative \chibThreeP decay is performed for the first time.
The obtained \Y3S fractions are 42 $\pm$ 12\stat${}^{+8.9}_{-11.6}\syst^{+2.7}_{-3.1}\systpol \%$ and 41 $\pm$ 8\stat${}^{+1.3}_{-8.6}\syst^{+2.6}_{-3.1}\systpol \%$ for \sqs=7 and 8 \tev, respectively. The measured \chiboneThreeP mass is $10{,}508 \pm 2\stat \pm
8\syst \mevcc$.


