\chapter*{Acknowledgements}
It would not have been possible to write this doctoral thesis without the help
and support of the kind people around me. I had a chance to work at the large
\lhcb collaboration where one works together with many people, and, unfortunately,
this means that the number of people that in some way have contributed to this
work is too large to all personally thank here.

I would like to express my special appreciation and thanks to Vanya Belyaev,
who was, as usual, full of nice ideas and useful comments. Your advice on
research as well as on the life itself have been priceless and this was my
fault, that sometimes I didn't follow them.

I would like to thank to my PhD advisors, Concezzio Bozzi and Hans Dijkstra,
the discussions and suggestions on multiple subjects concerning the analysis
were always useful. Thank you for guidance, understanding and patience.
Many thanks to smart people from ITEP LHCb group. Viktor Egorychev, Daria Savrina,
Ivan Polyakov, your comments and advice help a lot. Many thanks to the authors
of the previous \chib study. Konstantin Belous and Mikhail Shapkin, you work
helps a lot. Patric Robbe, thank  you for the help with Monte-Carlo simulation.


Concerning the work on the profiler I would like to thank Ben Couturier and
Marco Cattaneo for helping me with preparing the publication and given me an
opportunity to present my work at CHEP conference in New-York. And Marco
Clemencic, I could thank you for your help on software, in particular
concerning \gaudi.

Concerning the time at LHCb Online Team I would like to thank to all
team. Niko Neufeld, thank you for being my promoter and for taking risk of 
hiring me --- it was the first step in my past 7 years career at \cern.

Thank you to my colleagues from University of Ferrara. Stefania Vecchi and
Antonio Falavella, it was a pleasure to work with you.

There are still too many people to mentions. All the other people within \lhcb,
who helped, worked, drank coffee, ran Relay Race with me: thank you for the
good atmosphere.

I am really thankful to my parents for all their support during this long path,
starting from university and then working at \cern.

Finally, and most importantly, I would like to thank my wife Vika and daugther
Ira for their love and constant support, for all the late nights and early
mornings, and for keeping me sane over the past few months.

