\chapter{Conclusion}

In this thesis the following topics were addressed: 

\begin{enumerate}

\item A software profiling tool was developed. 
This profiling tool helps to analyze and improve the performance of the  
\lhcb software, with particular emphasis on the optimization of the 
High Level Trigger software. This tool is currently used within \lhcb.

\item  Measurements of the fractions of $\Upsilon$ mesons originating from \chib 
radiative decays in proton-proton collisions at \lhcb were obtained  
as a function of $\Upsilon$ transverse momentum in the rapidity range $2.0 <
y^{\Upsilon} < 4.5$. This study  was performed on a data set, corresponding to 
an integrated luminosity of 3\invfb, collected at  
centre-of-mass energies \sqs=7 and 8\tev by the \lhcb experiment. The \chib (1P, 2P, 3P) 
mesons were reconstructed in radiative decays to \Y1S, \Y2S and \Y3S. 
The results in this study extend the statistical precision of 
previous LHCb measurements and add considerably more decays and higher transverse
momentum regions.  The measurement of \Y3S fraction in radiative \chibThreeP
decay was performed for the first time.

\item A measurement of the $\chi_{b1}(3P)$ mass was  performed. The result is
in good agreement with a recent \lhcb unpublished study with converted photons.

\end{enumerate}

The software profiling tool is the subject of a publication in a peer-reviewed journal. The 
analysis of \chib radiative decays has been reviewed in \lhcb and will be the subject 
of a publication.   

